---
title: "Tangram gesture analysis"
authors: "Ashley Leung and Dan Yurovsky"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, cache = TRUE,
                      message = FALSE)
```

```{r load-libraries}
library(here)
library(janitor)
library(readxl)
library(ggthemes)
library(tidyboot)
library(tidyverse)
library(broom) 
library(broom.mixed)
library(lme4)
library(lmerTest)

theme_set(theme_few(base_size = 12))
```


```{r load data}
raw_data <- list.files(here("data/gesture"), ".*csv", full.names = T)
agedata <- read_csv(here("data/databaseid.csv")) %>%
  mutate(subid = as.character(subid))

read_data <- function(file) {
  
  data <- read_csv(file) %>%
    remove_empty("cols") %>%
    mutate(id = parse_number(basename(file))) %>%
    clean_names() %>%
    select(-c(childgesture_ordinal, childgesture_onset, childgesture_offset,
              parentgesture_ordinal, parentgesture_onset, parentgesture_offset))
}

data <- map(raw_data, read_data) %>%
  bind_rows() %>%
  left_join(agedata, by = c("id" = "database_id"))

```

```{r tidy data}

tidy_data <- data %>%
  select(-id) %>%
  rename(ctrial = childgesture_trial,
         ptrial = parentgesture_trial,
         cgesture = childgesture_gesture,
         pgesture = parentgesture_gesture,
         cbarrier = childgesture_barrier,
         pbarrier = parentgesture_barrier,
         cspeech = childgesture_speech,
         pspeech = parentgesture_speech) %>%
  mutate(cgesture = cgesture == "y",
         cbarrier = if_else(cbarrier == "a", 1, 0),
         cspeech = cspeech == "y",
         pgesture = pgesture == "y",
         pbarrier = if_else(pbarrier == "a", 1, 0),
         pspeech = pspeech == "y")

kid_data <- tidy_data %>%
  filter(!is.na(ctrial)) %>%
  select(-c(pgesture:ptrial)) %>%
  rename(gesture = cgesture,
         barrier = cbarrier,
         speech = cspeech,
         trial = ctrial) %>%
  mutate(person = "child")

parent_data <- tidy_data %>%
  filter(!is.na(ptrial)) %>%
  select(-c(cgesture:ctrial)) %>%
  rename(gesture = pgesture,
         barrier = pbarrier,
         speech = pspeech,
         trial = ptrial) %>%
  mutate(person = "parent")

all_data <- bind_rows(parent_data, kid_data) %>%
  mutate(age = as.factor(age))

```

# Gestures in parent-child communication

In a previous study, we invited parent-child pairs to play an interactive referential game. During the game, parents and children took turns describing novel tangram images to one another over multiple rounds. In this work, we examine the use of gestures in parents and children during the game, and ask whether gesture use differs between parents and children, and how patterns change over development.

```{r gesture use analysis}

# children's gestures

kid_gestures <- kid_data %>%
  group_by(age) %>%
  tidyboot_mean(gesture) %>%
  mutate(age = as.factor(age))

ggplot(kid_gestures, aes(x = age, y = empirical_stat, fill = age)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
  labs(y = "Proportion of gesture use",
       x = "Age")

kid_visible_gestures <- kid_data %>%
  group_by(age) %>%
  tidyboot_mean(barrier, na.rm = T)

kid_speech <- kid_data %>%
  group_by(age) %>%
  tidyboot_mean(speech, na.rm = T)

# parent's gestures

parent_gestures <- parent_data %>%
  group_by(age) %>%
  tidyboot_mean(gesture) %>%
  mutate(age = as.factor(age))

ggplot(parent_gestures, aes(x = age, y = empirical_stat, fill = age)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
  labs(y = "Proportion of gesture use",
       x = "Child age")

parent_visible_gestures <- parent_data %>%
  group_by(age) %>%
  tidyboot_mean(barrier, na.rm = T)

parent_speech <- parent_data %>%
  group_by(age) %>%
  tidyboot_mean(speech, na.rm = T)

# compare parent and children gestures

all_gestures <- all_data %>%
  group_by(person, age) %>%
  tidyboot_mean(gesture)

ggplot(all_gestures, aes(x = age, y = empirical_stat, fill = age)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
  facet_wrap(~ person) +
  labs(y = "Proportion of gesture use",
       x = "Child age")

all_visible_gestures <- all_data %>% 
  filter(gesture == T) %>%
  group_by(person, age) %>%
  tidyboot_mean(barrier)

ggplot(all_visible_gestures, aes(x = age, y = empirical_stat, fill = age)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
  facet_wrap(~ person) +
  labs(y = "Proportion of gestures above barrier",
       x = "Child age")

all_speech <- all_data %>%
  filter(gesture == T) %>% 
  group_by(person, age) %>% 
  tidyboot_mean(speech)

ggplot(all_speech, aes(x = age, y = empirical_stat, fill = age)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
  facet_wrap(~ person) +
  labs(y = "Proportion of gestures represented in speech",
       x = "Child age")

```

```{r models}

# kid model

kid_model <- kid_data %>%
  group_by(age, subid) %>%
  glmer(gesture ~ age + (1|subid), family = "binomial", data = .) %>%
  tidy() %>%
  filter(effect == "fixed")

# parent model

parent_model <- parent_data %>%
  group_by(age, subid) %>%
  glmer(gesture ~ age + (1|subid), family = "binomial", data = .) %>%
  tidy() %>%
  filter(effect == "fixed")

# overall model

overall_model <- all_data %>%
  group_by(person, age, subid) %>%
  glmer(gesture ~ person + age + (1|subid), family = "binomial", data = .) %>%
  tidy() %>% 
  filter(effect == "fixed")

```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
