---
title: "Similar Tangrams"
author: "Dan Yurovsky"
date: '`r Sys.Date()`'
output:
  html_document:
    toc: false
    number_sections: false
    theme: lumen
    toc_float: false
    code_folding: hide
---

```{r, message=FALSE, warning=FALSE, show = F}
library(here)
library(knitr)
library(tidytext)
library(tidyboot)
library(koRpus)
#install.koRpus.lang("en")
library(koRpus.lang.en)
library(ggthemes)
library(readxl)
library(janitor)
library(forcats)
library(tidyverse)
#devtools::install_github("mikabr/ggpirate")
library(ggpirate)
library(widyr)
library(tm)
library(lme4)

opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, 
               error = FALSE, cache = TRUE, tidy = FALSE)

theme_set(theme_classic(base_size = 14))
```

We compute some simple measures of linguistic complexity for each participant:

1. MTLD - Measures of Textual Lexical Diversity (McCarthy, P. M. & Jarvis, S., 2010). A measure of lexical diversity that is more robust to some of the issues of corpus size than others like Type Token Ratio

2. Types - Just a count of unique types. Has corpus size problems (must be non-decreasing), but less bad than TTR

3. AoA - adult estimates of age of acquisition of each word from Kuperman et al. (2012). Higher average AoA could be a proxy for more sophisticated language

4. Log Frequency - Log Frequency estimates of each word from the SUBTLEX-US corpus. less frequent words plausibly index more sophisticated language (Brysbaert, New, & Keuleers, 2012)

```{r read-subj-data, include = F, eval = F}
kid_files <- list.files(path = here("deidentified/"), pattern = "*[0-9].csv", 
                    full.names = TRUE)
adult_files <- list.files(path = here("deidentified/adult/"), pattern = "*[0-9].csv", 
                    full.names = TRUE)

  
ages <- read_csv(here("deidentified/meta.csv")) %>%
  mutate(age = as.character(age))

kid_data <- map_dfr(kid_files, read_csv) %>%
  left_join(ages, by = c("subid"))

adult_data <- map_dfr(adult_files, read_csv) %>%
  mutate(age = "adult")

data <- bind_rows(kid_data, adult_data)
```

```{r read-all-data}
combined_data <- read_csv(here("deidentified/combined.csv"))
exchanges_data <- read_csv(here("deidentified/combined.csv")) 
```

```{r read-corpus-data}
kuperman_aoas <- read_excel(
  here("corpus_data/AoA_ratings_Kuperman_et_al_BRM.xlsx")) %>%
  clean_names() %>%
  select(word, rating_mean, freq_pm) %>%
  mutate_at(vars(rating_mean, freq_pm), as.numeric) %>%
  mutate(log_freq = freq_pm) %>%
  rename(aoa = rating_mean) %>%
  select(-freq_pm)
```

```{r compute-lang-measures}
tokens <- combined_data %>%
  filter(role == "director") %>%
  group_by(age, person, subid, target, rep_num) %>%
  summarise(words = str_to_lower(utterance)) %>%
  unnest_tokens(word, words) %>%
  ungroup() %>%
  mutate(word = str_to_lower(word))

tokens <- exchanges_data %>%
  filter(role == "director") %>%
  group_by(age, person, subid, target, rep_num) %>%
  slice(1) %>%
  summarise(words = str_to_lower(utterance)) %>%
  unnest_tokens(word, words) %>%
  ungroup() %>%
  mutate(word = str_to_lower(word))


aoas <- tokens %>%
  left_join(kuperman_aoas, by = "word") %>%
  filter(!word %in% tm::stopwords()) %>%
  group_by(age, person, target, rep_num, subid) %>%
  summarise_at(vars(aoa, log_freq), ~mean(.x, na.rm = T)) %>%
  group_by(age, person, target, subid) %>%
  ungroup() %>%
  mutate(person = case_when(person == "left" ~ "adult",
                            person == "right" ~ "adult",
                            T ~ person))

mean_aoas <- aoas %>%
  group_by(age, person, rep_num, subid) %>%
  summarise_at(vars(aoa, log_freq), ~mean(.x, na.rm = T)) %>%
  tidyboot_mean(aoa, na.rm = T)

ggplot(mean_aoas, aes(x = rep_num, y = empirical_stat, color = as.factor(age))) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(.25)) + 
  facet_wrap(~ person) + 
  geom_line()
  
aoa_lm <- aoas %>%
  filter(person  == "parent") %>%
  lmer(aoa ~ age * rep_num + (rep_num | subid) + (1|target),
       control = lmerControl(optimizer = "bobyqa"),
       data = .)

aoa_lm %>%
  tidy() %>%
  filter(effect == "fixed")
```

```{r unused-measures, eval = F, include = F}
corpora <- tokens %>%
  group_by(age, person, subid) %>%
  summarise(corpus = paste(word, collapse = " ")) %>%
  group_by(age, person, subid) %>%
  nest() %>%
  mutate(corpus = map(data, ~koRpus::tokenize(.x$corpus, format = "obj", 
                                      lang = "en", tag = TRUE))) %>%
  select(-data)

mtlds <- corpora %>%
  mutate(mtld = map(corpus, ~MTLD(.x, quiet = TRUE)@MTLD$MTLD)) %>%
  select(-corpus) %>%
  unnest(cols = c(mtld))

types <- tokens %>%
  group_by(age, person, subid) %>%
  distinct(word) %>%
  summarise(types = n())

measures <- left_join(mtlds, types, by = c("age", "person", "subid")) %>%
  left_join(aoas, by = c("age", "person", "subid")) %>%
  pivot_longer(cols = c(mtld, types, aoa, log_freq), names_to = "measure", 
               values_to = "score") %>%
  ungroup() %>%
  mutate(age = as_factor(age),
         person = as_factor(person))

```

```{r compute-game-measures, eval = F, include = F}
game_data <- data %>%
  group_by(age, person, subid, trial) %>%
  distinct(correct)

acc_data <- game_data %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = mean(correct)) %>%
  mutate(type = "self")

other_acc_data <- acc_data %>%
  ungroup() %>%
  mutate(person = case_when(person == "child" ~ "parent",
                            person == "parent" ~ "child",
                            person == "left" ~ "right",
                            person == "right" ~ "left", 
                            T ~ as.character(NA))) %>%
  mutate(type = "other")

reduction_data <- data %>%
  filter(role == "director") %>%
  group_by(age, subid, person, trial, target) %>%
  summarise(utterance = str_to_lower(utterance)) %>%
  unnest_tokens(word, utterance) %>%
  group_by(age, subid, person, target, trial) %>%
  summarise(words = n()) %>%
  summarise(reduction = log(last(words)/first(words))) %>%
  group_by(age, subid, person) %>%
  summarise(reduction = mean(reduction)) %>%
  mutate(type = "self")

other_reduction_data <- reduction_data %>%
  ungroup() %>%
  mutate(person = case_when(person == "child" ~ "parent",
                            person == "parent" ~ "child",
                            person == "left" ~ "right",
                            person == "right" ~ "left", 
                            T ~ as.character(NA))) %>%
  mutate(type = "other")

game_measures <- left_join(acc_data, reduction_data) %>%
  pivot_longer(cols = c(correct, reduction), 
               names_to = "game_measure", values_to = "value") %>%
  bind_rows(left_join(other_acc_data, other_reduction_data) %>%
              pivot_longer(cols = c(correct, reduction), 
                           names_to = "game_measure", values_to = "value")) %>%
  ungroup() %>%
  mutate(age = factor(age))


```

```{r descriptives, fig.width = 6, fig.height= 6, eval = F, include = F}
ggplot(measures, aes(x = age, y = score, 
                  color = person, fill = person)) + 
  facet_grid(measure ~ ., scales = "free") + 
  geom_pirate(bars = FALSE, show.legend = TRUE) + 
  scale_color_ptol() + 
  scale_fill_ptol() + 
  theme(legend.position = c(.2, 1), legend.title = element_blank(),
        legend.direction = "horizontal")

```

```{r write_file, eval = F, include = F}
write_csv(measures, here("deidentified/lang_measures.csv"))
```

```{r eval = F, include = F}
comparison_data <- left_join(measures, game_measures)

correlations <- comparison_data %>%
#  mutate(person = if_else(person %in% c("left", "right"), "adult", person)) %>%
  group_by(age, person, type, measure, game_measure) %>%
  nest() %>%
  mutate(cortest = map(data, ~cor.test(.x$score, .x$value)),
         cor = map(cortest, ~.x$estimate),
         ci = map(cortest, ~.x$conf.int),
         ci_lower = map(ci, ~.x[1]),
         ci_upper = map(ci, ~.x[2])) %>%
  select(-data, -cortest, -ci) %>%
  unnest(cols = c(cor, ci_lower, ci_upper))

correlations %>%
  filter(game_measure == "correct") %>%
  ggplot(aes(x = age, y = cor, color = person)) + 
  facet_grid(type ~ measure) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                      position = position_dodge(.25)) + 
  scale_color_ptol() + 
  geom_hline(aes(yintercept = 0), linetype = "dashed")

correlations %>%
  filter(game_measure == "reduction") %>%
  ggplot(aes(x = age, y = cor, color = person)) + 
  facet_grid(type ~ measure) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                      position = position_dodge(.25)) + 
  scale_color_ptol() + 
  geom_hline(aes(yintercept = 0), linetype = "dashed")
  
```