---
title             : "Parents scaffold the formation of conversational pacts with their children"
shorttitle        : "Parents scaffold pacts"

author: 
  - name          : "Ashley Leung"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "XXXXX"
    email         : "XXXXX"
  - name          : "Robert D. Hawkins"
    affiliation   : "2"
  - name          : "Daniel Yurovsky"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "University of Chicago"
  - id            : "2"
    institution   : "Princeton Neuroscience Institute"
  - id            : "3"
    institution   : "Carnagie Mellon University"

abstract: |
   Adults readily form pacts, or temporary agreements about referent names, over the course of conversation. Young children fail to do so with peers, but recent evidence suggests that explicit feedback from adults may improve their performance. Do parents naturally provide such structure in their conversations with children? Using a director-matcher paradigm, we first show that parents and children (ages 4, 6, 8) converge on increasingly accurate and efficient conversational pacts. Further, parents of younger children provide more interactive feedback. Finally, we analyze asymmetries in parents' and children's contributions, finding that pacts tend to originate with the parent, but are simplified by younger children. Together, these results support the idea that parents sensitively adapt their language to their children's developmental level to scaffold successful communication.
   
authornote: |
  All data and code for these analyses are available at https://osf.io/3f8hy/?view_only=9a196db0444c4867bc899cc70a7a1e9c. Videos of experiment sessions are available on Databrary.

keywords          : "parent-child interaction; language development; communication"
wordcount         : "1385"
references        : "42"

bibliography      : ["tangram.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r load-packages, include = FALSE}
library(png)
library(grid)
library(egg)
library(xtable)
library(knitr)
library(papaja)
library(entropy)
library(ggthemes)
library(lme4)
library(lmerTest)
library(directlabels)
library(ggrepel)
library(here)
library(scales)
library(tidyboot)
library(broom)
library(broom.mixed)
library(kableExtra)
library(english)
library(ggthemes)
library(effectsize)
library(glue)
library(tidyverse)
library(tidytext)
library(textstem)
library(entropy)
library(janitor)

theme_set(theme_few(base_size = 10) + theme(legend.position = "none"))

knitr::opts_chunk$set(fig.pos = '!tb', echo = FALSE, cache = TRUE, 
                      warning = FALSE, message = FALSE, 
                      sanitize = TRUE, fig.path='figs/', fig.width = 3,
                      fig.height = 3, fig.pos = "t!")
set.seed(42)
options(digits=3, dplyr.summarise.inform = FALSE)
```

Effective communication relies on common ground, or shared knowledge, between conversational partners. To communicate successfully, interlocuters must understand each other and *know* that they understand each other [@bruner1985]. Conversations are thus a cooperative process, and even simple referential expressions are constructed collaboratively through negotiation. When the meaning of an utterance is unclear, or when an intended referent does not have a singular conventional label, interlocutors will engage in negotiation, arriving at a *conversational pact* about how to think and talk about the intended referent [@clark1986]. These conversational pacts are temporary agreements for referent names, and adults fluently form, revise, and track the formation of pacts. For instance, Brennan and Clark [-@brennan1996] showed that adults will use the appropriate level of specificity for a referent (e.g. "loafer" rather than "shoe" when another shoe is present), carry this forward into a new context with the same conversational partner even when the initial competitor is removed, then revert to "shoe" when a new partner is introduced. Conversational pacts are thus *partner-specific*, further suggesting that pacts are formed for the purpose of in-the-moment communicative success between conversational partners.

While adults readily form conversational pacts with one another, children struggle substantially both to establish and to deploy conversational pacts with peers. In a series of studies, Krauss and Glucksberg [-@krauss1977] asked pairs of age-matched children to play a director-matcher game that required them to refer to novel objects [see also @krauss1969]. Across repeated interactions with the same novel objects, 5- and 6-year-old children showed very little evidence of pact formation: The matcher's accuracy in selecting the correct referent remained low, and the director did not reduce of the length of their referential expressions as adults do. Older children showed some improvement on both measures, but even 10- and 11-year-olds were less successful than a comparison group of adults. These results are perhaps surprising, given that children participate in conversation at much younger ages. What might contribute to children's apparent failure to collaboratively construct conversational pacts with one another?

The first possibility is that children struggle to produce referential expressions that are comprehensible to others. Indeed, evidence suggests that young children do not reliably produce sufficiently informative referring expressions, and may not be able to identify when an expression is underinformative [@asher1976, @robinson1977]. As such, children may generate referential expressions for novel objects that are overly idiosyncratic, or simply insufficiently informative for their conversational partner to correctly identify the intended referent. At the same time, young children may have trouble seeking clarification or providing feedback to their conversational partners when necessary [@anderson1994]. Therefore, when interacting with peers, children may face difficulties in producing informative referential expressions and in seeking sufficient clarification when needed.

While children struggle as directors, their performance can improve significantly when an adult offers explicit guidance on whether their referential expressions are ambiguous or otherwise insufficiently informative. For example, @deutsch1982 showed that clarification questions could be used by adults to eventually elicit unambiguous descriptions from 6- and 9-year-olds and, to a lesser extent, from 3-year-olds. A recent training study by @matthews2007 replicated this finding in 2- to 4-year-olds, and further showed transfer to a different communication task. While these studies show how adult input may help children produce informative referential expressions, it remains unclear whether, or how, adults provide such feedback in the course of natural adult-child conversations.

Children engage in conversation with their caregivers from their second year of life and reciprocal social interaction even before that [@bruner1985]. Further, children's language development is predicted most strongly not by the amount of language they hear, but rather by the amount of conversational turns they engage in [@romeo2018]. Given that young children struggle with informativity and perspective-taking, how do conversations with caregivers succeed? One possibility is that parents naturally adopt some of the strategies used by experimenters in training studies of conversational pact formation: Pointing out when references are ambiguous, clarifying when children have produced insufficient information, and/or helping children to conceptualize their referential targets in better ways. Indeed, parents' contingent responses to children's incorrect or incomplete utterances have been implicated in language learning more broadly [@chouinard2003]. 

Parents spend a tremendous amount of time with children, and often have quite accurate models of their children's lexical and conceptual knowledge [@fenson1994]. Prior work has shown that parents leverage their knowledge of their children's vocabularies to calibrate the informativeness of their referential expressions [@leung2019]. Do they also leverage this knowledge to scaffold the formation of conversational pacts with children? In this study, we asked parents and their 4-, 6-, and 8-year-old children, as well as pairs of adults, to play an adapted version of Krauss and Glucksberg's [-@krauss1969] director-matcher game. We analyzed their interactions to ask (1) whether parents' contributions support the formation of conversational pacts, (2) what strategies parents use to support pact formation, and (3) whether the nature of these pacts changes over development as children acquire more language.

```{r child = "sections/parent-child.Rmd"}
```

```{r child = "sections/comprehension.Rmd"}
```

```{r child = "sections/production.Rmd"}
```

# Discussion

The ability to collaborate with conversational partners on intended meaning is crucial for successful communication. It may be especially important to achieve successful communication with *children*, who regularly encounter novel objects and situations they do not yet have precise words for. In this study, we used a classic repeated reference game to investigate the collaborative processes at play in interactions between parents and their children. While children often struggle to succeed in such games with their peers, we found that even young children were able to successfully form referential pacts with their parents: Accuracy increased, fewer turns were taken, and utterances gradually became shorter over the course of interaction. Furthermore, our results exposed key differences in parental behavior across ages: parents of younger children engaged in more conversational turns, asked more questions, produced longer referential expressions per turn, and adopted less complex labels. These findings indicate that parents may spontaneously adopt some of the strategies used in training studies [e.g. @matthews2007] to scaffold pact formation with their children.

Our results also contribute to the debate over why children may struggle to form referential pacts with each other. One family of explanations has suggested that children simply cannot take their partner's perspective into account, and produce references only they understand [@krauss1977], or cannot judge which expressions are more informative in the first place, even for themselves [@robinson1977; @asher1976]. An alternative account is that errors may partly arise from children's difficulty in the role of  matcher: They may struggle to provide sufficient feedback to their partner or ask for clarification when it is necessary [@anderson1994].

While we find some support for each of these accounts in our data, our analysis of the asymmetry in the introduction of pacts suggests an additional possibility: Young children may simply be unable to supply a good enough label on their own, possibly due to limited expertise in identifying and labeling the most informative features of novel objects. Once presented with an appropriate label from a parent, however, they will readily adopt and use it. In this way, the processes underlying the mutual "learning" of referential pacts, in the service of coordinating on meaning with a specific partner, may be the same as those underlying language acquisition. Thus the everyday interaction of parents and children trying to understand one another may not only scaffold local pact formation, but support communicative development more broadly.

# Acknowledgements

This research was funded by James S. McDonnell Foundation Scholar Award in Understanding Human Cognition \#220020506 to DY.

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
