---
title             : "Parents scaffold the formation of conversational pacts with their children"
shorttitle        : "Parents scaffold pacts"

author: 
  - name          : "Ashley Leung"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "XXXXX"
    email         : "XXXXX"
  - name          : "Robert D. Hawkins"
    affiliation   : "2"
  - name          : "Daniel Yurovsky"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "University of Chicago"
  - id            : "2"
    institution   : "Princeton Neuroscience Institute"
  - id            : "3"
    institution   : "Carnegie Mellon University"

abstract: |
   Adults readily form pacts, or temporary agreements about referent names, over the course of conversation. Young children fail to do so with peers, but recent evidence suggests that explicit feedback from adults may improve their performance. Do parents naturally provide such structure in their conversations with children? Using a director-matcher paradigm, we first show that parents and children (ages 4, 6, 8) converge on increasingly accurate and efficient conversational pacts. Further, parents of younger children provide more interactive feedback. Finally, we analyze asymmetries in parents' and children's contributions, finding that pacts tend to originate with the parent, but are simplified by younger children. Together, these results support the idea that parents sensitively adapt their language to their children's developmental level to scaffold successful communication.
   
authornote: |
  All data and code for these analyses are available at https://osf.io/3f8hy/?view_only=9a196db0444c4867bc899cc70a7a1e9c. Videos of experiment sessions are available on Databrary.

keywords          : "parent-child interaction; language development; communication"
wordcount         : "1385"
references        : "42"

bibliography      : ["tangram.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r load-packages, include = FALSE}
library(png)
library(grid)
library(egg)
library(xtable)
library(knitr)
library(papaja)
library(entropy)
library(ggthemes)
library(lme4)
library(lmerTest)
library(directlabels)
library(ggrepel)
library(here)
library(scales)
library(tidyboot)
library(broom)
library(broom.mixed)
library(kableExtra)
library(english)
library(ggthemes)
library(effectsize)
library(glue)
library(tidyverse)
library(tidytext)
library(textstem)
library(entropy)
library(janitor)

# load in helper functions
box::use(./sections/helpers)
box::reload(helpers)

theme_set(theme_few(base_size = 10) + theme(legend.position = "none"))

knitr::opts_chunk$set(fig.pos = '!tb', echo = FALSE, cache = TRUE, 
                      warning = FALSE, message = FALSE, 
                      sanitize = TRUE, fig.path='figs/', fig.width = 3,
                      fig.height = 3, fig.pos = "t!")
set.seed(42)
options(digits=3, dplyr.summarise.inform = FALSE)
```

One of the core features of human language is it's incredible productivity [@hockett1960]. While we often think of words as having fixed meanings, and referents of having fixed labels, these are both substantial simplifications [@elman2009]. The same word can have different meanings in different contexts, and can take on new meanings over time. The same object can be a dog, a pug, an animal or Max. Children don't just learn the sounds, words, and structures of their native language---they learn how to *use language to communicate*.

Effective communication relies on common ground, or shared knowledge, between conversational partners. To communicate successfully, interlocutors must understand each other and *know* that they understand each other [@bruner1985]. Conversations are thus a cooperative process; even simple referential expressions are constructed collaboratively through negotiation. When the meaning of an utterance is unclear, or when an intended referent does not have a singular conventional label, interlocutors will engage in negotiation, arriving at a *conversational pact* about how to think and talk about the intended referent [@clark1986]. 

These conversational pacts are temporary agreements for referent names, and adults fluently form, revise, and track the formation of pacts. For instance, Brennan and Clark [-@brennan1996] showed that adults will use the appropriate level of specificity for a referent (e.g. "loafer" rather than "shoe" when another shoe is present), carry this forward into a new context with the same conversational partner even when the initial competitor is removed, then revert to "shoe" when a new partner is introduced. Conversational pacts are thus *partner-specific*, further suggesting that pacts are formed for the purpose of in-the-moment communicative success between conversational partners.

While adults readily form conversational pacts with one another, children struggle substantially both to establish and to deploy conversational pacts with peers. In a series of studies, Krauss and Glucksberg [-@krauss1977] asked pairs of age-matched children to play a director-matcher game that required them to refer to novel objects [see also @krauss1969]. Across repeated interactions with the same novel objects, 5- and 6-year-old children showed very little evidence of pact formation: The matcher's accuracy in selecting the correct referent remained low, and the director did not reduce of the length of their referential expressions as adults do. Older children showed some improvement on both measures, but even 10- and 11-year-olds were less successful than a comparison group of adults. These results are perhaps surprising, given that children participate in conversation at much younger ages. Why do children struggle to collaboratively construct conversational pacts with one another?

Problems in pact formation could step from three potential sources of difficulty: (1) comprehension, (2) production, and (3) negotiation and consensus formation. In order to be effective, a referential utterance has to solve two problems: (1) it must be a good enough description of the target object for the listener to identify it, and (2) it must be a poor description for other potential referents in the context. Children could be ineffective listeners who are bad at identify the right target based on the information in a referential utterance. Children could be underinformative producers who do not provide the right information in their referential utterances. Finally, children could have trouble negotiating with each-other to identify errors in comprehension and production and negotiate them.

One possibility is that children's difficulty in forming conventional pacts stems from issues in comprehension. In order to identify the target of an utterance, children need to be able to determine whether the information in it is a good description of each potential referent. Prior work shows that young children struggle to judge which referential expressions are more informative, even when making judgments about their own expressions [@asher1976, @robinson1977]. Children may thus struggle to identify the relevant and informative components of a complex utterance like "the shoe with the brown laces": they may think that any referent that matches on "shoe" is good enough. 

Alternatively, the primary source of difficulty might be the production of effective referential expressions. For novel objects, such as those studied by @krauss1977,  identifying the right features to refer to could be challenging for children without the scaffolding provided by a prior history of talking about the target object. For familiar objects, conventional labels provide a good default. However, conventional labels can insufficient in more challenging contexts, such as when a shoe should be called a "loafer" because of the presence of alternative shoes [@brennan1996]. Indeed, evidence suggests that young children do not reliably produce sufficiently informative referring expressions, and may not be able to identify when an expression is underinformative [@asher1976, @robinson1977]. The problem of successfully referring to novel referents may thus derive from one or both of these problems: children may generate referential expressions that are overly idiosyncratic, or simply insufficiently informative for their conversational partner to correctly identify the intended referent. 

Finally, children may struggle to communicate when they have not understood each-other. Adults readily use back-channels and affirmations to signal that they have understood a potentially ambiguous utterance, and will ask clarifying questions when they feel they have been unable to [@clark1986]. However, young children may have trouble seeking clarification or providing feedback to their conversational partners when necessary [@anderson1994]. As a consequence, children may not form the necessary common ground to communicate successfully with one another.

In a set of three studies, we measure the development of children's capacity with these three critical components of referential pact formation: comprehension, production, and negotiation. In Study 1, we simplified and adapted the classic paradigm developed by @clark1986 to measure conversational pact formation in parent-child dyads. While young children may struggle to communicate successfully with each-other, they spend many hours in conversation with parents and other caregivers. We studied these interactions to determine what kinds of converstional support parents provide their children over development in order to identify the aspects that are most challenging for young children in naturalistic settings. We found that even 4-year-old children and their parents can successfully communicate about novel objects, but that children's role in these conversations changed over development. For the youngest children, parents both provide significant scaffolding in negotiation and are the source of most of the informative features that constitute successful referential pacts. By the time children are 8-years-old, however, they take on a roughly equal share of referential pact construction. 

In Study 2, we asked an independent set of adults and children to use the utterances produced in these interactions to identify the target referents. This allowed us to isolate the utterances from the conversational contexts they are embedded in, and to independently measure children's developing comprehension. We found that the utterance produced by children in Study 1 were less informative than those produced by parents, but that child comprehenders were just as effective as adult comprehenders in identifying the referents of both parents' and children's utterances. 

Finally, in Study 3, we developed a novel production paradigm to identify 


```{r child = "sections/parent-child.Rmd"}
```

```{r child = "sections/comprehension.Rmd"}
```

```{r child = "sections/production.Rmd"}
```

# Discussion

The ability to collaborate with conversational partners on intended meaning is crucial for successful communication. It may be especially important to achieve successful communication with *children*, who regularly encounter novel objects and situations they do not yet have precise words for. In this study, we used a classic repeated reference game to investigate the collaborative processes at play in interactions between parents and their children. While children often struggle to succeed in such games with their peers, we found that even young children were able to successfully form referential pacts with their parents: Accuracy increased, fewer turns were taken, and utterances gradually became shorter over the course of interaction. Furthermore, our results exposed key differences in parental behavior across ages: parents of younger children engaged in more conversational turns, asked more questions, produced longer referential expressions per turn, and adopted less complex labels. These findings indicate that parents may spontaneously adopt some of the strategies used in training studies [e.g. @matthews2007] to scaffold pact formation with their children.

Our results also contribute to the debate over why children may struggle to form referential pacts with each other. One family of explanations has suggested that children simply cannot take their partner's perspective into account, and produce references only they understand [@krauss1977], or cannot judge which expressions are more informative in the first place, even for themselves [@robinson1977; @asher1976]. An alternative account is that errors may partly arise from children's difficulty in the role of  matcher: They may struggle to provide sufficient feedback to their partner or ask for clarification when it is necessary [@anderson1994].

While we find some support for each of these accounts in our data, our analysis of the asymmetry in the introduction of pacts suggests an additional possibility: Young children may simply be unable to supply a good enough label on their own, possibly due to limited expertise in identifying and labeling the most informative features of novel objects. Once presented with an appropriate label from a parent, however, they will readily adopt and use it. In this way, the processes underlying the mutual "learning" of referential pacts, in the service of coordinating on meaning with a specific partner, may be the same as those underlying language acquisition. Thus the everyday interaction of parents and children trying to understand one another may not only scaffold local pact formation, but support communicative development more broadly.

# Acknowledgements

This research was funded by James S. McDonnell Foundation Scholar Award in Understanding Human Cognition \#220020506 to DY.

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
