# Experiment 2: Comprehension

Our first experiment found that young children are able to coordinate on pacts with their parents.
Even four-year-olds readily adopted the labels introduced by their parents and interactively refined their descriptions in response to spontaneous parent-initiated repair.
So why do younger children struggle so much with their peers?
One possibility is that the difficulty lies primarily in the process of *comprehension*. 
Children might be poor listeners.
They may be unable to understand or accommodate their partner's description if it does not align with their own way of conceptualizing the tangram, preventing uptake of a pact.
Another possibility is that the root of the difficulty primarily lies in *production*.
In other words, children may have difficulty *generating* sufficiently descriptive referring expressions on their own, given their limited vocabulary and other processing constraints, but are able to recognize a good description when they hear it, and adopt that description going forward.

In Experiment 2, we tested the first of these two hypotheses using a comprehension task. 
We provided naive children and adults with the descriptions produced by participants in Experiment 1 and asked how well they were able to interpret them.
If comprehension is the root of the developmental problem, we might expect that naive children would be equally unable to interpret all referring expressions (regardless of whether they were originally produced by adults or children) while naive adults would have no difficulty.
Conversely, if naive children are able to understand the referring expressions produced by parents (and not necessarily those by children), then we may expect the source of the difficulty to be elsewhere.

```{r load-comprehension-data}
raw_adult_data <- read_csv(here("data/comprehension/comprehension_adults.csv"),
                           show_col_types = FALSE) %>%
  select(-age) %>%
  filter(!audioid %in% c("67_08", "67_08_b"))

check_correct <- raw_adult_data %>%
  filter(occurrence == "check") %>%
  mutate(check_correct = correct) %>%
  select(subid, check_correct)

passed_check <- check_correct %>%
  group_by(check_correct) %>%
  count() %>%
  pivot_wider(names_from = check_correct, values_from = n) %>%
  clean_names()

# kid data
stims <- read_csv(here("data/comprehension/random_stims.csv"),
                  show_col_types = FALSE) %>%
  select(-c(correct, trial, rightpic, leftpic))
```


```{r tidy-data}
# Note: our pre-processing pipeline started with raw, de-anonymized data. 
#       we have preserved this pipeline for reproducibility but only release the pre-processed data.

# database_ids <- read_csv(here("data/comprehension/databaseid.csv"), show_col_types = FALSE) %>%
#   rename(gameid = subid) %>%
#   select(gameid, age)

# raw_kid_data <- read_csv(here("data/comprehension/comprehension_kids.csv"), show_col_types = FALSE) %>%
#   filter(!is.na(id)) %>%
#   left_join(stims, by = c("id" = "subject", "target")) %>%
#   rename(audioid = audio,
#          trialnum = trial,
#          p_age = age) %>%
#   mutate(correct = correct=="Y") %>%
#   filter(!audioid %in% c("67_08", "67_08_b"))

# tidy_kid_data <- raw_kid_data %>%
#   separate(audioid, into = c("gameid", "gametrial"), sep = "_") %>%
#   mutate(gameid = as.numeric(gameid),
#          trial = as.numeric(gametrial)) %>%
#   left_join(database_ids, by = ("gameid")) %>%
#   mutate(log_rt = log(rt)) %>%
#   filter(rt < 10000) %>%
#   pivot_longer(cols = c(correct, rt, log_rt), names_to = "measure")
  
#write_csv(tidy_kid_data, 'data/comprehension/comprehension_kids_tidy.csv')

tidy_kid_data <- read_csv(here("data/comprehension/comprehension_kids_tidy.csv"))
```
# Methods

### Participants

`r passed_check$false + passed_check$true` adults (ages XXX) were recruited from Amazon Mechanical Turk.
Data from `r passed_check$false` pairs were dropped due to failure to complete the study, leaving a final sample of `r passed_check$true` pairs. 
Additionally, we planned to recruited a sample of 200 children from a preschool in the local community.
However, because of the COVID-19 pandemic, we were forced to terminate data collection early with only `r length(unique(tidy_kid_data$id))` children (ages `r min(tidy_kid_data$age)`-`r max(tidy_kid_data$age)`) .

### Stimuli 

We re-recorded all of the referring expressions produced in Exp. 1.

### Design and procedure

Each participants listened to exactly 10 recordings, one for each tangram.
On each trial, the target tangram appeared with the foil from Exp. 1.

### Pre-processing

```{r}
#gameid is original subject id
tidy_turk_data <- raw_adult_data %>%
  left_join(check_correct, by = c("subid")) %>%
  filter(check_correct, occurrence != "check") %>%
  separate(audioid, into = c("gameid", "gametrial"), sep = "_") %>%
  mutate(gameid = as.numeric(gameid),
         gametrial = as.numeric(gametrial)) %>%
  left_join(database_ids, by = ("gameid")) %>%
  mutate(log_rt = log(reactiontime)) %>%
  pivot_longer(cols = c(correct, reactiontime, log_rt), names_to = "measure")
```

```{r rt-skew}
ggplot(tidy_turk_data %>% filter(measure != "correct"), aes(x = value)) +
  facet_wrap(~ measure, scales = "free") + 
  geom_histogram()

ggplot(tidy_kid_data %>% filter(measure != "correct"), aes(x = value)) +
  facet_wrap(~ measure, scales = "free") + 
  geom_histogram()
```


## Results

Accuracy and RT as a function of age, person, occurrence

```{r descriptive-plots}
subj_data <- tidy_turk_data %>%
  filter(measure != "reactiontime") %>% #exclude 17
  group_by(age, person, occurrence, measure, gameid) %>%
  summarise(value = mean(value))

simple_effects <- subj_data %>%
  tidyboot_mean(value)

simple_effects %>% 
  ggplot(aes(x = as.factor(age), y = empirical_stat, color = person)) +
  facet_grid(measure ~ occurrence, scales = "free") + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(.5)) +
  theme_few()

#kid plots
kid_subj_data <- tidy_kid_data %>%
  filter(measure != "rt") %>% #exclude 17
  group_by(age, person, occurrence, measure, gameid) %>%
  summarise(value = mean(value))

kid_simple_effects <- kid_subj_data %>%
  tidyboot_mean(value)

kid_simple_effects %>% 
  ggplot(aes(x = as.factor(age), y = empirical_stat, color = person)) +
  facet_grid(measure ~ occurrence, scales = "free") + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(.5)) +
  theme_few()
```

Models from Pre-reg

We will fit a logistic mixed effects model predicting informativeness from person (parent/child), age of child in the pair (4, 6, 8), trial (1 vs 2) and all of their interactions.

```{r full-acc-lmer}
full_acc_lmer <- tidy_turk_data %>%
  filter(measure == "correct") %>%
  glmer(value ~ person * age * occurrence + 
                   (1|target) ,
       family = "binomial", data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

full_acc_lmer

#kid model

kid_full_acc_lmer <- tidy_kid_data %>%
  filter(measure == "correct") %>%
  glmer(value ~ person * age * occurrence + 
                   (1|target) ,
       family = "binomial", data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

kid_full_acc_lmer

```

```{r reduced-acc-lmer}
acc_lmer <- tidy_turk_data %>%
  filter(measure == "correct") %>%
  glmer(value ~ person + age + occurrence  + 
                   (1|target) + (1|subid), 
        family = "binomial", data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

acc_lmer

#kid model
kid_acc_lmer <- tidy_kid_data %>%
  filter(measure == "correct") %>%
  glmer(value ~ person + age + occurrence  + 
                   (1|target) + (1|subid), 
        family = "binomial", data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

kid_acc_lmer

#two-way
kid_two_way_lmer <- tidy_kid_data %>%
  filter(measure == "correct") %>%
  glmer(value ~ person*occurrence + age + 
                   (1|target) + (1|subid), 
        family = "binomial", data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

kid_two_way_lmer

```

```{r full-rt-lmer}
full_rt_lmer <- tidy_turk_data %>%
  filter(measure == "log_rt") %>%
  lmer(value ~ person * age * occurrence + 
                   (1|target) + (1|subid), data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

full_rt_lmer
```

```{r reduced-rt-lmer}
rt_lmer <- tidy_turk_data %>%
  filter(measure == "log_rt") %>%
  lmer(value ~ person + age + occurrence  + 
                   (1|target) + (1|subid), data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

rt_lmer
```


So parents' descriptions lead to more accurate and faster guesses. Both older kids and parents of older kids give better descriptions. 

But no effect of occurrence--descriptions on the second appearance of each item do not appear to contain less information for guessing the target.

```{r exchange-data}
exchange_data <- read_csv(here("data/exchange_data.csv")) %>%
  select(subid, trial, director, person, num_exchanges) %>%
  group_by(trial, subid) %>%
  summarise(num_exchanges = sum(num_exchanges))

turk_exchange_data <- tidy_turk_data %>% left_join(exchange_data, 
                                                   by = c("gameid" = "subid"),
                                                   "gametrial" = "trial")

turk_exchange_data %>%
  filter(measure == "correct") %>%
  group_by(age, num_exchanges, person) %>%
  summarise(value = mean(value)) %>%
  ggplot(aes(x = num_exchanges, y = value, color = as.factor(age))) +
  facet_wrap(~ person) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```