---
title: "Parents scaffold the formation of conversational pacts"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\ Department of Psychology, 1202 W. Johnson Street \\ Madison, WI 53706 USA
    \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\ Department of Educational Psychology, 1025 W. Johnson Street \\ Madison, WI 53706 USA}

abstract: >
    Adults readily form pacts, or temporary agreements about referent names, over the course of conversation. Young children do so less reliably with peers, but recent evidence suggests that explicit feedback from adults may improve their performance [@matthews2007]. The present study seeks to understand the role parents spontaneously play in scaffolding children's referential pact formation. How might children learn from the adults they interact with in daily life? In our experiment, we replicate Clark and Wilkes-Gibbs' [-@clark1986] findings with adult-adult and parent-child participant pairs using a modified matcher-director task. First, we show that that parents and children (ages 4, 6, 8) can interactively converge on increasingly accurate and efficient pacts over the course of the task, but that parents of younger children provide more interactive feedback. Second, we analyze asymmetries in alignment, finding that pacts tend to originate with the parent but are simplified by younger children. Taken together, these results support the idea that parents sensitively adapt their language use to their children's developmental level to scaffold successful communication.
    
keywords: >
    referential pacts; parent-child communication
    
output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
# Note: to build, 
```

```{r, libraries}
library(broom.mixed)
library(tidyboot)
library(png)
library(grid)
library(xtable)
library(ggthemes)
library(lme4)
library(lmerTest)
library(here)
library(tm)
library(tidytext)
library(tidyverse)

theme_set(theme_few(base_size = 12))

SCALE <- c("#9ecae1", "#4292c6", "#08519c", "black")
```

```{r load-data}
kuperman_aoas <- read_csv(here("corpus_data/kuperman_aoas.csv"))
combined_data <- read_csv(here("deidentified/combined.csv")) 
exchanges_data <- read_csv(here("deidentified/exchanges.csv")) 
```

Common ground is a foundational requirement for successful communication: Interlocutors must both understand each other and know that they understand each other [@clark1986; @bruner1985]. As a consequence, even simple referential expressions are constructed collaboratively. For instance, listeners will often provide a backchanel like "uh huh" to signal their understanding of a speaker's meaning. When the  meaning of an utterance is unclear, interlocutors will engage in negotiaton, arriving at a *conversational pact* about how to think and talk about the intended referent [@clark1986]. 

Adults form, revise, and track the formation of pacts fluently. For instance, Brennan and Clark [-@brennan1996] showed that adults will use the right level of specificity for a referent (e.g. "loafer" rather than "shoe" when another shoe is present), carry this forward into a new context with the same conversational partner even when the initial competitor is gone, but revert to "shoe" when a new partner is introduced.

Children, on the other hand, struggle significantly both to establish and to deploy converstational pacts. In a series of studies, Krauss and Glucksberg [-@krauss1969] asked pairs of age-matched children to play a matcher-director game in which success required them to form conversational pacts about novel objects [@glucksberg1966;@krauss1969;@krauss1977]. Across repeated interactions with the same novel objects, @krauss1969 measured two correlated measures of conceptual pact formation: Matcher's accuracy in selecting the correct referent, and reduction of the number of words produced by the director. @krauss1969 found that 5 and 6-year-old children showed very little evidence of success of on either measure, whereas older children both improved accuracy and reduced referential expression lengths over trials. However, even 10 and 11-year-olds were less successful than a comparison group of adults. 

Why do children struggle to form referential pacts? One possible reason is that young children cannot take into account a partner's perspective, and generate expressions that are informative only to themselves. Indeed, early evidence showed that young children who fail at referential tasks with peers can succeed on the same task when experimenters use referent names that were generated by the children themselves [@glucksberg1966]. Alternatively, children may fail to form referential pacts because they are insensitive to informativity in general, and thus cannot produce appropriately informative references [@beal1982]. This account is supported by studies that have found that children are unable to accurately judge the informativeness of messages, and that those who are poor communicators could not identify the correct referent from their own expressions after a two-week delay [@robinson1977; @asher1976]. Finally, the difficulty may partly arise from children's difficulty in the role of matcher: They may struggle to provide sufficient feedback to their partner or ask for clarification when it is necessary [@anderson1994; @garrod1993].

Although children struggled as directors in Krauss and Glucksberg's studies, their performance improved significantly when an adult offered them explicit guidance on whether their referential expressions were ambiguous or otherwise insufficiently informative. In addition, @deutsch1982 showed that clarification questions could be used by adults to eventually elicit unambiguous descriptions from 6- and 9-year-olds and, to a lesser extent, from 3-year-olds. A recent training study by @matthews2007 replicated this finding in 2- to 4-year-olds, and further showed transfer to a different communication task.

Despite these potential limitations, children engage in conversation with their caregivers from their second year of life [@bruner1985]. Further, children's language development is predicted most strongly not by the amount of language they hear, but rather by the amount of conversation with their caregivers they engage in [@romeo2018; @weisleder2013]. How do these conversations succeed, and scaffold learning, despite young children's difficulties in forming conversational pacts? One possiblity is that parents naturally adopt some of the strategies used by experimenters in training studies of conversational pact formation: Pointing out when references are ambiguous, clarifying when children have produced insufficient informaion, and/or helping children to conceptualize their referential targets in better ways. Indeed, parents' contingent responses to children's incorrect or incomplete utterances have been implicated in children's learning of both semantic and syntactic structures [@clark1997; @chouinard2003]. 

Parents spend a tremendous amount of time with children, and thus often have quite accurate models of their children's lexical and conceptual development [@fenson2007]. Prior work has shown that parents leverage their knowledge of their children's vocabularies to calibrate the informativeness of their refererring expressions [@leung2019]. Do they also leverage this knowledge to scaffold the formation of conversational pacts with children? We asked parents and their 4, 6, and 8-year-old children as well as a group of adults to play an adapted version of Krauss and Glucksberg's [-@krauss1969] matcher-director game. We then analyzed their interactions to ask (1) Whether parents' contributions support the formation of conversational pacts, (2) What strategies parents use to support the formation of these pacts, and (3) Whether parents contributions are tuned to their children's lexical development, changing from 4 to 8 years of age.

# Referential Communication Experiment

## Methods

```{r 2-col-image, fig.env = "figure", fig.pos = "t", fig.width=3.5, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Example of iPad screens for the director (left) and matcher (right) during the game."}
img <- png::readPNG("figs/display.png")
grid::grid.raster(img)
```

```{r acc_exchanges, cache=T, fig.env = "figure*", fig.pos = "t!", fig.width=7, fig.height=3, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "\\label{fig:acc_exchanges}(A) Accuracy improves over time for all groups. (B) Number of dialogue exchanges is higher for younger children. Error bars are 95\\% CIs. The drop in accuracy for 8-year-olds is likely an artifact of a small set of children losing interest in the task."}
# Note: this is moved up here to get the fig to appear on the right page... i know it's annoying.
d.accuracy.raw <- combined_data %>%
  ungroup() %>%
  mutate(age = as.character(age),
         age = if_else(is.na(age), 'adult', age)) %>%
  mutate(person = ifelse(person %in% c('left', 'right', 'parent'), 
                         'adult', person)) %>%
  group_by(subid, trial, age, target, rep_num) %>%
  summarize(correct = mean(correct)) %>% # make sure each trial is only counted once
  ungroup()

# Bootstrap error bars 
result.acc.means <-  d.accuracy.raw %>%
  group_by(age, rep_num) %>%
  tidyboot_mean(correct)

# render plot
plt.results.acc <- result.acc.means %>%   
  ggplot(aes(x = rep_num, y = empirical_stat * 100,  group = age, color = age)) +
    geom_line() +
    geom_errorbar(aes(ymin = ci_lower * 100, ymax = ci_upper * 100),
                  width = 0.05) +
    ylab("% accuracy") +
    xlab("repetition #") +
    ylim(78, 100) +
    theme(aspect.ratio = 1) +
    scale_color_manual(values = SCALE) +
    labs(tag = 'A')

lmer.accuracy <- d.accuracy.raw %>%
  filter(age != "adult") %>%
  mutate(age = as.numeric(age)) %>%
  glmer(correct ~ age + rep_num + (rep_num | subid) + (1 | target), 
                            family = 'binomial', data = .) %>%
  tidy()

age_effect_acc = lmer.accuracy %>% filter(term == 'age')
rep_effect_acc = lmer.accuracy %>% filter(term == 'rep_num')

d.exchanges.raw <- exchanges_data %>%
  mutate(age = as.character(age)) %>%
  mutate(age = if_else(is.na(age), 'adult', age)) %>%
  group_by(subid, trial, age, target, rep_num) %>%
  summarize(num_exchanges = n()) %>% 
  ungroup()

d.exchanges.mean <- d.exchanges.raw %>%
  group_by(age, rep_num) %>%
  tidyboot_mean(num_exchanges)

# Bootstrap error bars and render plot
plt.results.exchanges <-  d.exchanges.mean %>%
  ggplot(aes(x = rep_num, y = empirical_stat, color = age, group = age)) +
    geom_line() +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    ylab("# exchanges per round") +
    xlab("repetition #") +
    theme(aspect.ratio = 1) +
    scale_color_manual(values = SCALE) +
    labs(tag = 'B')

# Bootstrap error bars and plot
lmer.exchanges <- d.exchanges.raw %>% 
  filter(age != 'adult') %>%
  mutate(age = as.numeric(age)) %>%
  lmer(num_exchanges ~ age + rep_num +  (rep_num | subid) + (1 | target), 
       control = lmerControl(optimizer = "bobyqa"), data = .) %>%
  tidy()

age_effect_exchanges = lmer.exchanges %>% filter(term == 'age')
rep_effect_exchanges = lmer.exchanges %>% filter(term == 'rep_num')

gridExtra::grid.arrange(plt.results.acc, plt.results.exchanges, ncol = 2)
```

### Participants

Children (ages 4, 6, and 8) and their parents were recruited from a database of families in the local community to achieve a planned sample of 60 parent-child pairs.
A total of 75 children and their parents participated, but data from 12 pairs were dropped due to experimental error or failure to complete the study, leaving a final sample of 63 pairs.
Additionally, a control group of adult participants were recruited from the University of Chicago's online subject pool to achieve a planned sample of 20 adult-adult pairs.
At the time of analysis, data from 15 pairs was included.

### Stimuli 

Twelve solid black images of tangrams, and colored versions of the same tangrams, were selected from a database of Public Domain images. The tangram images were normed on Amazon Mechanical Turk (mTurk) for pairwise similarity. In order to construct a set that allowed for dissimilar tangrams to be paired together, two images were excluded based on similarity judgments, forming the final set of 10 images used for the study. The colored versions of the tangrams were not used for norming, but were used during the communicative game.

### Design and procedure

Each dyad played a cooperative game with iPads. Pairs sat at a table with a divider in the middle, which prevented participants from looking at each other's iPad screens during the game. The game was a simplified version of the matcher-director task used in @clark1986. Participants were told that they would take turns being the director and matcher. They were told that the director should describe the image inside the blue square, and the matcher should select an image based on the director's description. After instruction, the practice and experimental trials began. On each experimental trial, two solid black tangrams appeared on the iPad screens. The same images appeared on each screen, but their positions were randomized. On the director's screen, one image appeared inside a blue square, while the images on the matcher's screen simply appeared on a white background (Figure 1). Upon selection of an image on the matcher's screen, the selected image became colorful, and a sound was played (independent of accuracy). After each trial, the roles were switched. Practice trials followed the same structure as experimental trials, but images of fruits and vegetables were used during this round. 

There were 4 blocks of 10 trials. Each tangram appeared as the target once during each block, such that each tangram was the target four times during the game. Trials within blocks were randomized. The 10 tangrams were shuffled and randomly assigned to one of the participants at the beginning of the game. The assignment dictated who would be the director for a particular target in the first repetition block. Thus, each participant played the role of director two times for each of the 10 tangrams. In each round, the target tangram appeared with different foils. To ensure that the game would not be too difficult for young children, trials were constructed such that the most similar tangrams (based on mTurk worker judgments) did not appear together.

### Pre-processing

All sessions were videotaped, and the videos were transcribed using Datavyu--an Open-Source coding software [@datavyu-team2014]. Research assistants used videos of excluded pairs for training and practice. Each video was transcribed and checked by two different research assistants. To ensure anonymity of participants, names were transcribed as "yyy". Inaudible words were transcribed as "xxx". Each utterance was coded manually as either being part of a trial, or being unrelated to the game (e.g. parents requesting children to sit down, talking about where were going after the session, etc.), with unrelated utterances removed before analysis.

## Results

```{r reduction, cache=T, fig.env = "figure*", fig.pos = "t!", fig.width=7, fig.height=3, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "\\label{fig:reduction}Total number of words in referring expressions produced by children and parents over the course of interaction."}
d.reduction.raw <- exchanges_data %>%
  mutate(age = ifelse(is.na(age), 'adult', age),
         num_words =  str_count(utterance, " ") +1) %>%
  filter(role == 'director') %>%
  mutate(person = ifelse(person %in% c('left', 'right', 'parent'), 'adult', person)) %>%
  group_by(age, rep_num, person, target, subid, trial) %>%
  summarize(numExchanges = n(),
            num_words = sum(num_words)) %>%
  mutate(normalized_num_words = num_words / numExchanges) %>%
  ungroup() 

d.reduction.means <- d.reduction.raw %>% 
  group_by(age, rep_num, person) %>%
  tidyboot_mean(normalized_num_words) %>%
  mutate(plot_person = if_else(person == "adult", "adult", age))

reduction_labels = tibble(rep_num = c(3.5, 3.5), empirical_stat = c(14, 6), 
                          person = c("adult", "child"), 
                          plot_person = c("adult", "4"),
                          age = c("4", "4"))

d.reduction.means %>%
  ggplot(aes(x = rep_num, y = empirical_stat, 
             group = person, color = plot_person, label = person)) +
  geom_line() +
  facet_grid(. ~ age) + 
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
  geom_text(data = reduction_labels)+
  theme_few() +
  theme(aspect.ratio = 1, legend.position = "none") +
  ylab("# words per exchange") +
  xlab("rep #") +
  scale_color_manual(values = SCALE)
```

```{r}
word_exchange_cor = round(cor(d.reduction.raw$numExchanges, d.reduction.raw$num_words),2)

d.reduction.centered <- d.reduction.raw %>% 
  filter(age != 'adult') %>% 
  group_by(subid, person) %>%
  mutate(age = as.numeric(age) - 6,  
         rep_num = as.numeric(rep_num) - 2.5,
         ordinal_rep = if_else(rep_num == first(rep_num), 
                               'first', 'second'))

lmer.reduction.controlled <-  d.reduction.centered %>%  
  lmer(log(normalized_num_words) ~ person * age * rep_num + 
         (1 + rep_num * person | subid) + (1 + rep_num | target), 
       data = ., contrasts = list(person = contr.sum), 
       control = lmerControl('bobyqa')) %>%
  tidy() %>%
  filter(effect == 'fixed')
```

```{r}
age_effect_reduction = lmer.reduction.controlled %>% filter(term == 'age')
age_effect_reduction_pvalue <- round(age_effect_reduction$p.value, 3)
age_effect_reduction_pvalue <- ifelse(age_effect_reduction_pvalue < 0.001, 
                               '< 0.001', paste0(c('=', age_effect_reduction_pvalue), collapse = ' '))

rep_effect_reduction = lmer.reduction.controlled %>% filter(term == 'rep_num')
rep_effect_reduction_pvalue <- round(rep_effect_reduction$p.value, 3)
rep_effect_reduction_pvalue <- ifelse(rep_effect_reduction_pvalue < 0.001, 
                               '< 0.001', paste0(c('=', rep_effect_reduction_pvalue), collapse = ' '))

person_effect_reduction = lmer.reduction.controlled %>% filter(term == 'person1')
person_effect_reduction_pvalue <- round(person_effect_reduction$p.value, 3)
person_effect_reduction_pvalue <- ifelse(person_effect_reduction_pvalue < 0.001, 
                               '< 0.001', paste0(c('=', person_effect_reduction_pvalue), collapse = ' '))

person_age_interaction_reduction = lmer.reduction.controlled %>% filter(term == 'person1:age')
person_age_interaction_reduction_pvalue <- round(person_age_interaction_reduction$p.value, 3)
person_age_interaction_reduction_pvalue <- ifelse(person_age_interaction_reduction_pvalue < 0.001, 
                               '< 0.001', paste0(c('=', person_age_interaction_reduction_pvalue), collapse = ' '))

person_rep_interaction_reduction = lmer.reduction.controlled %>% filter(term == 'person1:rep_num')
person_rep_interaction_reduction_pvalue <- round(person_rep_interaction_reduction$p.value, 3)
person_rep_interaction_reduction_pvalue <- ifelse(person_rep_interaction_reduction_pvalue < 0.001, 
                                                  '< 0.001', paste0(c('= ', person_rep_interaction_reduction_pvalue), collapse = ' '))

age_rep_interaction_reduction = lmer.reduction.controlled %>% filter(term == 'age:rep_num')
age_rep_interaction_reduction_pvalue = round(age_rep_interaction_reduction$p.value, 3)
age_rep_interaction_reduction_pvalue <- ifelse(age_rep_interaction_reduction_pvalue < 0.001, 
                                                  '< 0.001', paste0(c('= ', age_rep_interaction_reduction_pvalue), collapse = ' '))

person_age_rep_interaction_reduction = lmer.reduction.controlled %>% filter(term == 'person1:age:rep_num')
person_age_rep_interaction_reduction_pvalue = round(person_age_rep_interaction_reduction$p.value, 3)
person_age_rep_interaction_reduction_pvalue <- ifelse(person_age_rep_interaction_reduction_pvalue < 0.001, 
                                                  '< 0.001', paste0(c('= ', person_age_rep_interaction_reduction_pvalue), collapse = ' '))
```

We characterized developmental differences using three measures of communicative behavior.
First, we examined accuracy to evaluate whether children were able to succeed at the reference game in collaboration with their parents. Second, we examined conversational turn-taking behavior to evaluate how interactive dialogue may contribute to success. Third, we examined the number of words produced by each partner on each turn to evaluate the contributions of children of different ages to the development of efficient pacts.

### Performance accuracy

We began by analyzing task performance across age groups.We constructed a mixed-effects logistic regression model predicting whether the matcher successfully chose the correct referent on each trial. The model included fixed effects of age and repetition block, random intercepts for each tangram and pair of participants, and random effects of repetition block for each pair of participants (\texttt{correct $\sim$ age + rep + (rep | subj) + (1 | tangram)}). 

While accuracy was initially well above chance at all age groups, we found a significant main effect of age ($b$ = `r round(age_effect_acc$estimate, 2)`, $t$ = `r round(age_effect_acc$statistic, 2)`; $p = 0.003$):  Pairs containing younger children performed significantly more poorly than pairs containing older children. Critically, however, accuracy improved significantly over the four repetition blocks for all groups ($b$ = `r round(rep_effect_acc$estimate, 2)`, $t$ = `r round(rep_effect_acc$statistic, 2)`, $p < 0.001$; see Fig. \ref{fig:acc_exchanges}A). Such improvement for 4-year-olds contrasts with early results of communication between age-matched children, which found no improvement in accuracy with kindergardeners [age 5, @glucksberg1966;@krauss1969]. 

### Interactive dialogue exchanges

```{r}
questionMarks <- exchanges_data %>% 
  filter(person == 'parent', role == 'matcher') %>% 
  mutate(containQ = str_detect(utterance, "\\?")) %>% 
  rowwise() %>%
  mutate(age = paste0(c('age', age), collapse = "")) %>%
  group_by(age, containQ) %>% 
  tally() %>% 
  group_by(age) %>%
  mutate(proportion = n / sum(n)) %>%
  ungroup()

questionMarkProportions <- questionMarks %>%
  filter(containQ) %>%
  select(age, proportion) %>%
  pivot_wider(names_from = age, values_from = proportion)

chisq.out <- questionMarks %>% 
  select(age, containQ,n) %>%
  spread(containQ,n) %>% 
  select(-age) %>%
  chisq.test() %>%
  tidy()
```

If the ability of children of different ages to successfully establish reference in both director and matcher roles depends on scaffolding provided by their parents, we would expect additional dialogue turns for younger children. We counted the total number of exchanges on each trial, defined as the number of distinct turns of continuous speech. We then constructed a mixed-effects regression model predicting the continuous number of exchanges with the same effect structure as reported in the previous section.Consistent with previous work in adults [@clark1986], we found a significant main effect of repetition ($b$ = `r round(rep_effect_exchanges$estimate, 2)`, $t$ = `r round(rep_effect_exchanges$statistic, 2)`; $p < 0.001$).
Fewer dialogue turns were required on later trials.

However, we also found a significant main effect of the child's age ($b$ = `r round(age_effect_exchanges$estimate, 2)`, $t$ = `r round(age_effect_exchanges$statistic, 2)`; $p < 0.001$). Pairs with 4-year-old children took roughly one additional turn at each point in the experiment than pairs with older children, who more closely resembled pairs of adults (see Fig. \ref{fig:acc_exchanges}B). This increased level of interactivity between parents and younger children provides an interesting contrast with previous studies showing decreased interactivity in pairs of younger children [@garrod1993; @anderson1994].

These lengthier exchanges may reflect efforts by parents to provide and elicit additional clarification or confirmation, or may simply reflect attentional difficulties. As a rough estimate of the content of parents' dialogue responses when their child was the director, we counted the number of question marks in the transcript^[Because questions were not always annotated with a question mark, this represents a lower bound on the true estimate of questions.].
We found `r round(questionMarkProportions$age4, 2) * 100`% of responses to 4-year-olds contained question marks, compared to `r round(questionMarkProportions$age6, 2) * 100`% and `r round(questionMarkProportions$age8, 2) * 100`% to 6 and 8-year-olds, respectively ($\chi^2(2)=$ `r round(chisq.out$statistic,2)
`, $p < 0.001$).

### Reduction in length of referring expression

A key signature of successful communication among adults is an increase in efficiency over repeated reference [@krauss1964;@clark1986]. 
As pairs form conceptual pacts, they are able to communicate the same meaning using fewer words. 
We asked whether parents and children of different ages spontaneously reduce their referring expressions in the same way.
Because the total number of words produced on a trial is correlated with the number of dialogue exchanges examined above ($r=$ `r word_exchange_cor`), we constructed a a normalized efficiency measure that controls for additional turns.
Specifically, we defined efficiency as the total number of words produced by the *director* divided by the number of dialogue exchanges on that trial. 

Because participants in a pair alternated roles, each participant served as the director twice for each tangram. 
This structure allowed us to examine how each participant changed their language when they were the director (Fig. \ref{fig:reduction}). 
Using a mixed-effects model, we predicted the (log) number of words per exchange on each trial, including fixed effects of child age group, repetition block, and speaker identity (parent vs. child) as well as all of their interactions.
We also included random intercepts at the tangram-level and maximal random structure at the dyad level [i.e. intercept, slopes for repetition block and speaker identity, and their interaction; @BarrLevyScheepersTily13_KeepItMaximal].
All variables were centered to allow interpretation of lower-order terms as effects at the average level of the other terms. 
We found significant main effects of repetition block ($t =$ `r round(rep_effect_reduction$statistic,2)`, $p$`r age_rep_interaction_reduction_pvalue`), speaker identity ($t =$ `r round(person_effect_reduction$statistic,2)`, $p$ `r person_effect_reduction_pvalue`), and age ($t =$ `r round(age_effect_reduction$statistic,2)`, $p$ `r age_effect_reduction_pvalue`).
All else being equal, directors use fewer words over subsequent repetitions, children use fewer words than their parents, and pairs with older children use fewer words than pairs with younger children.

However, these main effects were clarified by several interactions of interest.
First, while parents on average used more words as director than their children did, we found a significant interaction with the child's age group ($t =$ `r round(person_age_interaction_reduction$statistic,2)`, $p$ `r  person_age_interaction_reduction_pvalue`).
This gap between parent and child utterance length is largest at 4 years but nearly disappeared by 8 years. 
Second, we find that parents reduced their utterance length over time more strongly than children did, holding age group constant ($t =$ `r round(person_rep_interaction_reduction$statistic,2)`, $p$ `r person_rep_interaction_reduction_pvalue`).
Third, having older children in a pair supported stronger reduction overall, ($t =$ `r round(age_rep_interaction_reduction$statistic,2)`, $p$ `r age_rep_interaction_reduction_pvalue`). 
Finally, an intriguing developmental question is whether reduction changes over the course of development: are 4-year-olds able to become more efficient as common ground is built in the same way 8-year-olds do?
Because parents of different age groups display similar slopes of reduction, this question is addressed by a 3-way interaction. 
We found that this interaction was not significant ($t=$ `r round(person_age_rep_interaction_reduction$statistic, 2)`, $p$ `r person_age_rep_interaction_reduction_pvalue`), although our sample was likely underpowered to detect this higher-order interaction. 


# Analyzing the content of pacts

```{r origins, cache=T, fig.env = "figure*", fig.pos = "t!", fig.width=7, fig.height=4, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "\\label{fig:origins}(A) Probability of words used on final round first occuring with child or parent. (B) Complexity of language used by different age groups. Error bars are 95\\% CI."}
matches <- read_csv('../../deidentified/word_matches.csv') %>% 
  filter(later_rep == 4) %>%
  spread(earlier_rep, match) %>%
  mutate(first_appearance = case_when(`1` ~ '1', 
                                      `2` ~ '2', 
                                      `3` ~ '3', 
                                      TRUE ~ 'never'),
         total = length(first_appearance),
         director = final_round_person,
         matcher = case_when(final_round_person == 'left' ~ 'right',
                             final_round_person == 'right' ~ 'left',
                             final_round_person == 'parent' ~ 'child',
                             final_round_person == 'child' ~ 'parent')
   ) %>%
  filter(first_appearance != 'never') %>%
  mutate(introduced_by = ifelse(first_appearance %in% c('2'), director, matcher),
         #introduced_by_parent = introduced_by == 'parent',
         introduced_on_first_round = first_appearance %in% c('1'),
         introduced_by_self = introduced_by == director,
         introduced_by_other = introduced_by != director,
          director = ifelse(director %in% c('left', 'right'), 'adult', director),
         age = ifelse(is.na(age), 'adult-adult', age)
         )

origins.plt1 <- matches %>%
  group_by(age, director) %>%
  tidyboot_mean(introduced_by_other) %>%
  #tally() %>%
  ggplot(aes(x = as.character(age), y = empirical_stat, 
             group = director, color = director)) +
    geom_line() +
    geom_point() +
    geom_hline(yintercept = .5) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    theme_few() +
    theme(legend.position="top") +
    ylab('% words introduced by partner') +
    xlab("child age group") +
    theme(aspect.ratio = 1) +
    guides(color=guide_legend(title="Director")) +
    scale_color_colorblind(breaks=c("child", "parent")) +
    labs(tag = 'A')

tokens <- combined_data %>%
  filter(role == "director") %>%
  group_by(age, person, subid, target, rep_num) %>%
  summarise(words = str_to_lower(utterance)) %>%
  unnest_tokens(word, words) %>%
  ungroup() %>%
  mutate(word = str_to_lower(word))

aoas <- tokens %>%
  left_join(kuperman_aoas, by = "word") %>%
  filter(!word %in% tm::stopwords()) %>%
  group_by(age, person, target, rep_num, subid) %>%
  summarise(aoa = mean(aoa, na.rm = T)) %>%
  group_by(age, person, target, subid) %>%
  ungroup() %>%
  mutate(person = case_when(person == "left" ~ "adult",
                            person == "right" ~ "adult",
                            T ~ person))

mean_aoas <- aoas %>%
  group_by(age, person, rep_num, subid) %>%
  summarise(aoa = mean(aoa, na.rm = T)) %>%
  tidyboot_mean(aoa, na.rm = T)

origins.plt2 <- ggplot(mean_aoas %>% filter(person != "adult"), aes(x = rep_num, y = empirical_stat, color = as.factor(age))) +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  facet_wrap(~ person) + 
  geom_line() + 
  theme(aspect.ratio = 1, legend.position = "none") +
  scale_color_colorblind() + 
  labs(x = "rep #", y = "AoA (average)", tag = "B")

cowplot::plot_grid(origins.plt1, origins.plt2, ncol = 2, rel_widths =  c(1/3, 2/3))
```

Pairs of age-matched children are notoriously poor at repeated referential communication [@glucksberg1966], failing to coordinate on mutually comprehensible referring expressions.
Our results demonstrate that when children perform the same task with their parents, this coordination problem can be solved: they converge on increasingly accurate and efficient pacts, as adults do. 
What, then, allows children to coordinate with their parents but not with their peers? 

One possibility is that children lack the ability to *adapt* to their partner: they have a strong preference for a particular idiosyncratic description and are not sensitive to the possibility that their partner may not understand it. 
Under this hypothesis, children fail with other children because they each continue to use mutually incomprehensible expressions, and only succeed with their parent as a result of the parent's flexibility.
An alternative possibility is that young children are able to adapt but are uncertain about what an appropriate label would be in the first place.
They fail with other children because neither can generate an understandable enough initial label to start the pact-formation process, but will quickly pick up on a good label supplied by their parent. 

These accounts make different predictions about who is adapting to who: do pacts originate with children, or with adults?
We distinguish these accounts by quantitatively analyzing the natural-language transcripts. 

## Where do pacts come from?

```{r}
match.model <- matches %>% 
  filter(experiment == 'adult-child') %>% 
  mutate(age = as.numeric(age) - 6) %>%
  glmer(introduced_by_other ~ age * director + (1 | target) +  (1 | subid), 
        contrasts = list(director = contr.sum),
        data = .,
        control=glmerControl('bobyqa'),
        family = 'binomial') %>%
  tidy()

speaker_effect <- match.model %>% filter(term == 'director1')
match.interaction_effect <- match.model %>% filter(term == 'age:director1')
```

For each word in the final description of a tangram, we checked whether it had appeared in an earlier referring expression for that tangram in the same pair. 
We noted the first trial where it appeared, and who was director when it was produced^[To match across different word forms (e.g. "jumping" vs. "jumped") we first lemmatized each word. We also filtered out stop words ("the", "with"), as well as common words that weren't part of the pacts ("person", "box"), and excluded words that were appearing for the first time on the final repetition.].
The proportion of words originating with the child and parent is shown in Fig. \ref{fig:origins}.
We observed an asymmetry: the words used by children on the final repetition block are more likely to have originated with their parents than the words used by parents were to originate with their children.
In addition, this gap appeared to close with older groups, with parents more likely to adopt words introduced by older children.

We tested this hypothesized interaction using a mixed-effects logistic model predicting whether each word appearing in the final repetition block was introduced by the current director or by their partner.
We included fixed effects of age group and the speaker identity (parent or child), as well as random intercepts for each pair of participants and each tangram.
We found a significant main effect of speaker identity, with the words used by children more likely to originate with their partner than the words used by parents, $t=$ `r round(speaker_effect$statistic, 2)`, $p < 0.001$.
Additionally, we found a weak but significant interaction, $t=$ `r round(match.interaction_effect$statistic, 2)` $p=$ `r round(match.interaction_effect$p.value,2)`.

## How do pacts differ across ages?

Given that the labels used by younger children tend to originate with their parents, it is tempting to conclude that adaptation for these pairs is entirely one-sided.
It is possible, however, that the resulting pacts are nonetheless shaped by children.
In particular, we suggest that even though young children may not be able to *supply* good initial labels, they may serve as "regularizers" or "filters" that constrain the complexity of the resulting pact, since it must pass through their comprehension and production system.

In order to estimate the complexity of language used by participants, we used self-reported age of acquisition estimates collected by @kuperman2012. 
These researchers asked almost 2000 Mechanical Turkers to judge the age at which they first acquired each of a large set of words on a 7 point Likert scale. 
Although one might be suspicious that adults have little access to this kind of information, these judgments are highly correlated with parents' estimates of the age at which their children learn corresponding words, and are better than a variety of other measures (e.g. frequency, concreteness, word length) in predicting lexical decision times [@kuperman2012].

For each participant, on each trial, we estimated the linguistic complexity of their contribution by averaging the estimated age of acquisition for each word in their utterance^[We first removed any words in a list of `r stopwords() %>% length()` stopwords like "at" and "me" from the \texttt{tm} package [@feinerer2008]`. These effects are shown in Fig. \ref{fig:origins}B.

# Discussion

We found reduction in length of referring expressions in both adult and parent-child participant pairs (Fig. 3), replicating Clark and Wilkes-Gibbs' [-@clark1986] results. While the main effect of reduction was present across all age groups, we found developmental changes in the number of conversational turns. Specifically, four-year-olds and their parents had significantly more dialogue exchanges throughout the game. Finally, we found that children were more likely to use labels generated by their parents, and not vice versa, suggesting that parents were not simply accepting their children's labels in order to achieve communicative success.

Our results show that children as young as 4 are able to cooperate with a more linguistically capable partner to form conceptual pacts in conversation, in line with Glucksberg and Krauss' [-@glucksberg1967] research showing communicative success in experimenter-child interactions. Importantly, our study extends previous work to show that even without scripts or pre-written prompts, parents can provide helpful feedback naturally to scaffold referential success with their young children.

What are some ways parents may be providing feedback? While all pairs were able to converge on more efficient reference over time, 4-year-olds and their parents took significantly more conversational turns on each trial. Responses to 4-year-olds were more likely to be questions, suggesting that parents could be asking for clarification in those conversational turns. This finding indicates that parents may use some of the strategies seen in training studies (e.g. @matthews2007) when engaging in referential communication with their young children.

Parents also produced longer referring expressions than children overall, suggesting that parents may be providing more information to ensure communicative success. Furthermore, parents of 4-year-olds produced more speech than parents in other age groups. This indicates that parents not only provide more information for their children in general, but that they are sensitive to *how much* information to give based on their children's developmental level.

Finally, we asked *who* initiated the referential pacts, to further understand how parents may be scaffolding communicative success with young children. In our predictions, we suggested two possible accounts of parent adaptation: 1) parents would adapt to young children by adopting more of their children's labels; 2) parents would provide higher-level feedback in order to scaffold referential success. Our analyses show that the labels children use are more likely to have originated from their parents, providing support for the latter account. That is, parent-child pairs are not achieving success due to parents accepting all labels provided by young children. Instead, our evidence points to parents offering feedback and perhaps suggesting more informative labels as factors leading to communicative success. It is entirely possible that the former account would also lead to communicative success, but our results indicate that parents do not naturally adopt that strategy, and instead opt to scaffold their young children's communicative skills. 

While children eventually become skilled conversationlists, little work has been done to understand *how* they acquire their communicative skills. Our study shows that children as young as four, who fail to reliably form conversational pacts with peers, can do so with a caregiver. Specifically, our work showcases that parents may naturally adopt useful strategies to guide children's conversational pact formation, and that may scaffold children's communicative development.


# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.

# References 

```{r}

# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
