---
title: "\\LARGE Parents scaffold the formation of conversational pacts with their children (SOM-R)"
# author: "\\large \\emph{Ashley, Leung, Alexandra Tunkel, and Daniel Yurovsky}"
author: "\\large \\emph{XX, XX, and XX}"
header-includes:
  - \usepackage[section]{placeins}
  - \usepackage{float}
  - \floatplacement{figure}{h!} # make every figure with caption = t
  - \raggedbottom
output: 
  pdf_document:
    latex_engine: xelatex
    number_sections: true
documentclass: article
bibliography: tangramgame-si.bib
fontsize: 11pt
geometry: margin=1in
csl: apa6.csl
---

```{r load-libraries, message=FALSE, warning=FALSE, include = F}
library(here)
library(knitr)
library(papaja)
library(kableExtra)
library(tidyverse)
library(tidyboot)
library(lme4)
library(lmerTest)
library(broom)
library(broom.mixed)
library(effectsize)
library(glue)
library(ggthemes)

opts_chunk$set(message = FALSE, warning = FALSE, error = FALSE, cache = TRUE, 
               tidy = FALSE, echo = FALSE)

theme_set(theme_few(base_size = 12))

options(digits=3)
```

\renewcommand\thesection{S\arabic{section}}
\renewcommand{\thetable}{S\arabic{table}}  
\renewcommand{\thefigure}{S\arabic{figure}}

\section{Norming Experiment}

To construct the "close" and "far" conditions, we required an estimate of the extent to which different tangrams would elicit similar names.
We recruited $XXX$ adult participants to provide one-word names for $YYY$ tangrams, each presented in isolation.
This distribution of names was intended to reflect the  "prior" over valid labels that adults might bring into a reference game. 
We then generated close (and far) pairs to maximize (and minimize) naming similarity using the following algorithm.

First, we computed the naming similarity between all pairs of stimuli, using the same metric reported in the main text.
For each target tangram $t$, we then found the unique distractors $d_{close} = \arg \min_{t'}s(t, t')$ and $d_{far} = \arg \max_{t'} s(t, t')$ and computed the range $T(t) = |s(t, d_{far}) - s(t, d_{close})|$. 
We then picked the single target with largest range and added it to our stimulus set, along with its close and far distractors.
We then removed all three tangrams $\{t, d_{close}, d_{far}\}$ from the overall set, and repeated this procedure until we obtained 10 unique, non-overlapping sets to use in our production study.

\section{Additional comprehensibility analyses}

\subsection{Response times are faster for parent descriptions}

Because accuracy was near ceiling, we also considered the measure of response time.
We find that descriptions produced by parents lead to faster guesses, but there is still no effect of experiment phase.

```{r full-rt-lmer}
full_rt_lmer <- tidy_turk_data %>%
  filter(measure == "log_rt") %>%
  lmer(value ~ person * age * occurrence + 
                   (1|target) + (1|subid), data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

```

```{r reduced-rt-lmer}
rt_lmer <- tidy_turk_data %>%
  filter(measure == "log_rt") %>%
  lmer(value ~ person + age + occurrence  + 
                   (1|target) + (1|subid), data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

```

\subsection{Comprehensibility decreases with exchange length}

Finally, we consider whether descriptions produced in the context of a long back-and-forth exchange tend to be less comprehensible (see Appendix). 
We analyze this relationship that we didn't have room for in the main text.

```{r exchange-data}
turk_exchange_data <- d.exchanges.raw %>% 
  group_by(trial, subid) %>% 
  summarise(num_exchanges = sum(num_exchanges)) %>% 
  right_join(tidy_turk_data, by = c("subid" = "gameid"), "trial" = "gametrial")

turk_exchange_data %>%
  filter(measure == "correct") %>%
  group_by(age, num_exchanges, person) %>%
  summarise(value = mean(value)) %>%
  ggplot(aes(x = num_exchanges, y = value, color = as.factor(age))) +
  facet_wrap(~ person) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```

\newpage

\section*{References}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\noindent
<div id = "refs"></div>
\endgroup