---
title: "Language use in tangrams"
author: "Robert Hawkins, Ashley Leung, and Dan Yurovsky"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: false
    number_sections: false
    theme: lumen
    toc_float: false
    code_folding: hide
---

## Imports 

```{r, message=FALSE, warning=FALSE, show = F}
library(tidyverse)
library(tidyboot)
library(janitor)
library(lme4)
library(lmerTest)
library(broom)

theme_set(theme_classic(base_size = 18))
```

## Origin of final descriptions

For each (contentful & lemmatized) word in the final utterance, we can look at which earlier rounds, if any, it appeared in.

```{r}
# read_csv('../deidentified/word_matches.csv') %>%
#   gather(round, match, `1_match`, `2_match`, `3_match`) %>%
#   separate(round, into = c('round', 'garbage'), sep = '_') %>%
#   group_by(subid, age, final_round_person, round) %>%
#   summarize(match_rate = mean(match)) %>%
#   ungroup() %>%
#   mutate(match_target = ifelse(round == '2', 'same', 'diff'),
#          final_round_person = ifelse(final_round_person == 'child', 'child-last', 'parent-last')) %>%
#   group_by(final_round_person, age, round, match_target) %>%
#   tidyboot_mean(match_rate) %>%
#   ggplot(aes(x = round, y = empirical_stat)) +
#     geom_bar(stat = 'identity') +
#     facet_grid(final_round_person ~ age) +
#     geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
#     theme_bw() +
#     ylab('% final-round words occurring on round')
# 
# ggsave('appearance_on_earlier_rounds.pdf', width = 4, height = 3)
```

Are kids more likely to not re-use words (e.g. on final round using words never used before?)

```{r}
read_csv('../deidentified/word_matches.csv') %>%  
  group_by(age, final_round_person, experiment) %>%
  mutate(first_appearance = case_when(`1_match` ~ '1', 
                                      `2_match` ~ '2', 
                                      `3_match` ~ '3', 
                                      TRUE ~ 'never'),
         total = length(first_appearance),
         director = final_round_person,
         matcher = ifelse(final_round_person == 'parent', 'child', 'parent')) %>%
  group_by(age, director, experiment) %>%
  summarize(no_reuse = mean(first_appearance == 'never')) %>%
    ggplot(aes(x = as.factor(age), y = no_reuse, fill = director)) +
    geom_bar(stat = 'identity', position = 'dodge') +
    #facet_grid(age ~ director) +
    theme_bw() +
    ylab('% final-round words occurring on round')


```

Look at *first* round final words appear.

```{r}
matches <- read_csv('../deidentified/word_matches.csv') %>%  
  mutate(first_appearance = case_when(`1_match` ~ '1', 
                                      `2_match` ~ '2', 
                                      `3_match` ~ '3', 
                                      TRUE ~ 'never'),
         total = length(first_appearance),
         director = final_round_person,
         matcher = case_when(final_round_person == 'left' ~ 'right',
                             final_round_person == 'right' ~ 'left',
                             final_round_person == 'parent' ~ 'child',
                             final_round_person == 'child' ~ 'parent')
   ) %>%
  filter(first_appearance != 'never') %>%
  mutate(introduced_by = ifelse(first_appearance %in% c('2'), director, matcher),
         #introduced_by_parent = introduced_by == 'parent',
         introduced_on_first_round = first_appearance %in% c('1'),
         introduced_by_self = introduced_by == director,
         introduced_by_other = introduced_by != director,
          director = ifelse(director %in% c('left', 'right'), 'adult', director),
         age = ifelse(is.na(age), 'adult-adult', age)
         )

matches %>%
  group_by(age, director) %>%
  tidyboot_mean(introduced_by_other) %>%
  #tally() %>%
  ggplot(aes(x = as.character(age), y = empirical_stat, 
             group = director, color = director)) +
    geom_line() +
    geom_point() +
    geom_hline(yintercept = .5) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    theme_few() +
    ylab('% final-round words introduced by other') +
    xlab("child age group") +
    theme(aspect.ratio = 1) +
    guides(color=guide_legend(title="Director on final round")) +
    scale_color_colorblind(breaks=c("child", "parent")) 

ggsave('introduction.pdf', width = 5, height = 5)
```

```{r}
summary(glmer(introduced_by_other ~ age * director + (1 | target) +  (1 | subid), 
              data = matches %>% 
                filter(experiment == 'adult-child') %>% 
                mutate(age = as.numeric(age)), 
              family = 'binomial'))
```

## Look at local 'stickiness'



# Supplementary 

## Look at inverse


```{r}
read_csv('../deidentified/inverse_word_matches.csv') %>%  
  group_by(experiment, subid, target, age, person, rep_num) %>%
  summarize(any_match = any(final_match)) %>%
  # mutate(final_agent = ifelse(first_appearance %in% c('2', '4'), director, matcher),
  #        introduced_by_parent = introduced_by == 'parent',
  #        introduced_by_self = introduced_by == director) %>%
  filter(rep_num < 4) %>%
  group_by(experiment, age, person) %>%
  tidyboot_mean(col  = any_match) %>%
  rename(introduced_by = person) %>%
  ggplot(aes(x = as.character(age), y = empirical_stat, 
             group = introduced_by, color = introduced_by)) +
    geom_point() +
    geom_line() +
    geom_hline(yintercept = .5) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
   #facet_wrap(~ age) +
    theme_bw() +
    ylab('Probability of any words going on to end') +
    xlab("child age group") +
    theme(aspect.ratio = 1)

```

```{r}
summary(lmer(any_match ~ person * age + (1 | subid),  data = read_csv('../deidentified/inverse_word_matches.csv') %>%  
  group_by(experiment, subid, target, age, person, rep_num) %>%
  summarize(any_match = any(final_match)) %>% filter(experiment != 'adult-adult')))
```

## Look at informativity

```{r}
read_csv('../deidentified/informativity.csv') %>%
  filter(tfidf != 0) %>%
  mutate(num_tangrams_occurred_with =  round(1 / ((2^tfidf) /10))) %>%
  filter(word != 'zzz') %>%
  group_by(num_tangrams_occurred_with, initial_round_person) %>%
  tidyboot_mean(final_match) %>%
  rename(sample_size = n) %>%
  ggplot(aes(x = as.integer(num_tangrams_occurred_with), y = empirical_stat)) +
    geom_point(aes(size = sample_size), stat = 'identity') +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.1) +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F) +
    facet_wrap(~ initial_round_person) +
    #ylim(0, .22) +
    ylab('% appearing in final utterance') +
    xlab('distinctiveness of word in initial utterance (# tangrams)') +
    xlim(0,12) +
    scale_x_continuous(breaks = c(1,3, 5,7,9,11))+
    #theme_few() +
    theme(aspect.ratio = 1)
```


```{r}
read_csv('../deidentified/informativity.csv') %>%
  filter(tfidf != 0) %>%
  group_by(subid, age, word, person, rep_num) %>%
  mutate(num_tangrams_occurred_with =  round(1 / ((2^tfidf) /10))) %>%
  summarize(num_tangrams_occurred_with = mean(num_tangrams_occurred_with)) %>%
  ungroup() %>%
  mutate(rep_num = paste0('repetition ', rep_num)) %>%
  group_by(person, rep_num, age) %>%
  tidyboot_mean(num_tangrams_occurred_with) %>%
  ggplot(aes(x = age, y = empirical_stat, color = person)) +
    geom_line(stat = 'identity') +
    facet_grid(~ rep_num) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    theme_bw() +
    ylab('# tangrams words occur with') +
    ylim(1, 2.5) +
    theme(aspect.ratio = 1)

ggsave('informativity_mean.pdf', width = 8, height = 3)
```

```{r}
summary(lmer(num_tangrams_occurred_with ~ person + rep_num + age + (1 | subid),
     data = read_csv('../deidentified/informativity.csv') %>%
  filter(tfidf != 0) %>%
  group_by(subid, age, word, person, rep_num) %>%
  mutate(num_tangrams_occurred_with =  round(1 / ((2^tfidf) /10))) %>%
  summarize(num_tangrams_occurred_with = mean(num_tangrams_occurred_with))))
```

```{r}
read_csv('../deidentified/informativity.csv') %>%
  filter(tfidf != 0) %>%
  group_by(subid, age, target, person, rep_num) %>%
  mutate(num_tangrams_occurred_with =  round(1 / ((2^tfidf) /10))) %>%
  summarize(num_tangrams_occurred_with = min(num_tangrams_occurred_with)) %>%
  ungroup() %>%
  mutate(rep_num = paste0('repetition ', rep_num)) %>%
  group_by(person, rep_num, age) %>%
  tidyboot_mean(num_tangrams_occurred_with) %>%
  ggplot(aes(x = age, y = empirical_stat, color = person)) +
    geom_line(stat = 'identity') +
    facet_grid(~ rep_num) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    theme_bw() +
    ylab('maximum informativity per message') +
    ylim(1, 1.7) +
    theme(aspect.ratio = 1)

ggsave('min_per_message.pdf', width = 8, height = 3)

```

## Sanity checks

check for coding errors

```{r}
raw_data %>% 
  group_by(subid, trial) %>% tally() %>% filter(n == 1) %>% select(-n) %>% # get trial #s with 1 event
  left_join(raw_data) %>%
  group_by(person) %>% tally()

checking <- raw_data %>% 
  group_by(subid, trial) %>% tally() %>% filter(n == 1) %>% select(-n) %>% # get trial #s with 1 event
  left_join(raw_data) %>%
  group_by(person)
```