---
title: "Tangram comprehension analysis"
author: "Ashley Leung, Robert Hawkins, and Dan Yurovsky"
date: '`r Sys.Date()`'
output: 
  html_document:
  toc: false
number_sections: false
theme: lumen
toc_float: false
code_folding: hide
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, cache = TRUE,
                      message = FALSE)
```

```{r load-libraries}
library(here)
library(janitor)
library(readxl)
library(ggthemes)
library(tidyboot)
library(tidyverse)
library(broom) 
library(broom.mixed)
library(lme4)
library(lmerTest)

theme_set(theme_few(base_size = 12))
```

```{r load-data}
raw_turk_data <- read_csv(here("data/comprehension/dataFromMongo.csv")) %>%
  select(-age) %>%
  filter(!audioid %in% c("67_08", "67_08_b"))

check_correct <- raw_turk_data %>%
  filter(occurrence == "check") %>%
  mutate(check_correct = correct) %>%
  select(subid, check_correct)

passed_check <- check_correct %>%
  group_by(check_correct) %>%
  count() %>%
  pivot_wider(names_from = check_correct, values_from = n) %>%
  clean_names()
```

We kept `r passed_check$true` out of `r passed_check$true + passed_check$false` participants.

```{r tidy-data}
database_ids <- read_csv(here("data/databaseid.csv")) %>%
  rename(gameid = subid) %>%
  select(gameid, age)

tidy_turk_data <- raw_turk_data %>%
  left_join(check_correct, by = c("subid")) %>%
  filter(check_correct, occurrence != "check") %>%
  separate(audioid, into = c("gameid", "gametrial"), sep = "_") %>%
  mutate(gameid = as.numeric(gameid),
         gametrial = as.numeric(gametrial)) %>%
  left_join(database_ids, by = ("gameid")) %>%
  mutate(log_rt = log(reactiontime)) %>%
  pivot_longer(cols = c(correct, reactiontime, log_rt), names_to = "measure")
```

```{r rt-skew}
ggplot(tidy_turk_data %>% filter(measure != "correct"), aes(x = value)) +
  facet_wrap(~ measure, scales = "free") + 
  geom_histogram()
```


## Results

Accuracy and RT as a function of age, person, occurrence

```{r descriptive-plots}
subj_data <- tidy_turk_data %>%
  filter(measure != "reactiontime") %>% #exclude 17
  group_by(age, person, occurrence, measure, gameid) %>%
  summarise(value = mean(value))

simple_effects <- subj_data %>%
  tidyboot_mean(value)

simple_effects %>% 
  ggplot(aes(x = as.factor(age), y = empirical_stat, color = person)) +
  facet_grid(measure ~ occurrence, scales = "free") + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(.5)) +
  theme_few()
```

Models from Pre-reg

We will fit a logistic mixed effects model predicting informativeness from person (parent/child), age of child in the pair (4, 6, 8), trial (1 vs 2) and all of their interactions.
```{r full-acc-lmer}
full_acc_lmer <- tidy_turk_data %>%
  filter(measure == "correct") %>%
  glmer(value ~ person * age * occurrence + 
                   (1|target) ,
       family = "binomial", data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

full_acc_lmer
```

```{r reduced-acc-lmer}
acc_lmer <- tidy_turk_data %>%
  filter(measure == "correct") %>%
  glmer(value ~ person + age + occurrence  + 
                   (1|target) + (1|subid), 
        family = "binomial", data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

acc_lmer
```

```{r full-rt-lmer}
full_rt_lmer <- tidy_turk_data %>%
  filter(measure == "log_rt") %>%
  lmer(value ~ person * age * occurrence + 
                   (1|target) + (1|subid), data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

full_rt_lmer
```

```{r reduced-rt-lmer}
rt_lmer <- tidy_turk_data %>%
  filter(measure == "log_rt") %>%
  lmer(value ~ person + age + occurrence  + 
                   (1|target) + (1|subid), data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

rt_lmer
```


So parents' descriptions lead to more accurate and faster guesses. Both older kids and parents of older kids give better descriptions. 

But no effect of occurrence--descriptions on the second appearance of each item do not appear to contain less information for guessing the target.
